---
title: "Report Template coursework assignment A - 2021"
subtitle: "CS4125 Seminar Research Methodology for Data Science"
author: "Thomas Bos (), Daniël van Gelder (4551028), Jessie van Schijndel"
date: "20/04/2021"
output:
   pdf_document:
      fig_caption: true
      number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


\tableofcontents


# Part 1 - Design and set-up of true experiment 


## The motivation for the planned research 
(Max 250 words)
The coronavirus pandemic has had a great impact on many aspects of society. University education, in particular, has changed significantly. As education in many countries has shifted from physical lectures to online teleconferencing lectures, concerns have been raised with regards to the effectiveness of this method of education. While the technological developments surrounding teleconferencing have enabled an almost seamless transition from offline to online education, it may be that the lack of a physically present lecturer may affect the comprehensibility of the lecture material for students. With this research, we aim to address whether the students' understanding of the lecture material is affected by a different learning setting (i.e., from home watching an online lecture). The results may reveal whether online education is a way to move forward out of the pandemic. Moreover, if the results indicate no significant change in student understanding of material it may open up the way for new form of education, where students could enroll into "digital universities" without needing to be present at any time.

## The theory underlying the research  
(Max 250 words) Preferable based on theories reported in literature


## Research questions 
Our research question is 'What 
The research question that will be examined in the experiment (or alternatively the hypothesis that will be tested in the experiment)


## The related conceptual model 
This model should include:
*Independent variable(s)
*Dependent variable
*Mediating variable (at least 1)
*Moderating variable (at least 1)

The following sections describe the conceptual model for each type of variable:

### Independent Variable (IV)
The IV of this research is whether the participant (student) attends the lecture physically or from home through online teleconferencing. 

### Dependent Variable (DV)
The DV of this research is the relative score increase on the test that students make. Before the experiment the participants make a small test regarding the lecture material for which the score is expected to be low as the participants are expected to have no prior knowledge regarding the material. Then after the lecture the students make the same test regarding the lecture material. The relative increase (or unlikely decrease) of score will be the DV.

### Mediating Variable
As the students perform the test in a different setting (from home or on campus) depending on the IV. The change in setting is expected to have a mediating effect on the relationship  between the IV and DV.

### Moderating Variable
There are several factors which may a moderating effect on the relationship between the IV and the DV which are difficult control on the experiment. These mostly have to do with the environment in which the lecture is attended. The following list describes the specific variables which are believed to have this moderating effect:

- (online lecture) video/audio quality
- (online lecture) device that is used to attend lecture (e.g. laptop, tablet, smartphone)
- (both physical and online lecture) presence of noise and/or distraction in environment of watching lecture


## Experimental Design 
Note that the study should have a true experimental design

## Experimental procedure 
Describe how the experiment will be executed step by step


## Measures
In the experiment, both participant groups will take a pre-test and a post-test. This test aims to evaluate the participants' comprehension of the lecture material. The pre-test is meant to serve as a baseline measurement to rule out any pre-existing knowledge of the participants. Both tests will be identical and will be in the form of a multiple choice exam of ten questions to be taken in a short time span (10 minutes). The score of the test is defined as the proportion of correct answers. The measure of the experiment is the ratio between these to tests for each particpant: the score of the post-test divided by the score of the pre-test. 

## Participants
Describe which participants will recruit in the study and how they will be recruited

## Suggested statistical analyses
Describe the statistical test you suggest to care out on the collected data

# Part 2 - Generalized linear models

## Question 1 Twitter sentiment analysis (Between groups - single factor) 

### Conceptual model
Make a conceptual model for the following research question: Is there a difference in the sentiment of the tweets related to the different celebrities?

### Collecting tweets, and data preparation
Include the annotated R script (excluding your personal Keys and Access Tokens information), but put echo=FALSE, so code is not included in the output pdf file.


```{r, echo=FALSE, message=FALSE, warning=FALSE, include = FALSE}

#during writing you could add "eval = FALSE",  kntr will than not run this code chunk (take some time do)

setwd("~/OneDrive/Documents/MSc/Q4/Seminar Research Methodology for Data Science/coursework A") 
# apple , note use / instead of \, which used by windows


#install.packages("twitteR", dependencies = TRUE)
library(twitteR)
#install.packages("RCurl", dependencies = T)
library(RCurl)
#install.packages("bitops", dependencies = T)
library(bitops)
#install.packages("plyr", dependencies = T)
library(plyr)
#install.packages('stringr', dependencies = T)
library(stringr)
#install.packages("NLP", dependencies = T)
library(NLP)
#install.packages("tm", dependencies = T)
library(tm)
#install.packages("wordcloud", dependencies=T)
#install.packages("RColorBrewer", dependencies=TRUE)
library(RColorBrewer)
library(wordcloud)
#install.packages("reshape", dependencies=T)
library(reshape)

################### functions

  
clearTweets <- function(tweets, excl) {
  
  tweets.text <- sapply(tweets, function(t)t$getText()) #get text out of tweets 

  
  tweets.text = gsub('[[:cntrl:]]', '', tweets.text)
  tweets.text = gsub('\\d+', '', tweets.text)
  tweets.text <- str_replace_all(tweets.text,"[^[:graph:]]", " ") #remove graphic
  
  
  corpus <- Corpus(VectorSource(tweets.text))
  
  corpus_clean <- tm_map(corpus, removePunctuation)
  corpus_clean <- tm_map(corpus_clean, content_transformer(tolower))
  corpus_clean <- tm_map(corpus_clean, removeWords, stopwords("english"))
  corpus_clean <- tm_map(corpus_clean, removeNumbers)
  corpus_clean <- tm_map(corpus_clean, stripWhitespace)
  corpus_clean <- tm_map(corpus_clean, removeWords, c(excl,"http","https","httpst"))
  

  return(corpus_clean)
} 


## capture all the output to a file.

################# Collect from Twitter

# for creating a twitter app (apps.twitter.com) see youtube https://youtu.be/lT4Kosc_ers
#consumer_key <-'your key'
#consumer_scret <- 'your secret'
#access_token <- 'your access token'
#access_scret <- 'your access scret'

source("your_twitter.R") #this file will set my personal variables for my twitter app, adjust the name of this file. use the provide template your_twitter.R

setup_twitter_oauth(consumer_key,consumer_scret, access_token,access_scret) #connect to  twitter app


##### This example uses the following 3 celebrities: Donald Trump, Hillary Clinton, and Bernie Sanders
##  You should replace this with your own celebrities, at least 3, but more preferred 
##  Note that it will take the computer some to collect the tweets

tweets_T <- searchTwitter("#trump", n=300, lang="en", resultType="recent") #300 recent tweets about Donald Trump, in English (I think that 1500 tweets is max)
tweets_C <- searchTwitter("#hillary", n=300, lang="en", resultType="recent") #300 recent tweets about Hillary Clinton
tweets_B <- searchTwitter("#bernie", n=300, lang="en", resultType="recent") #300 recent tweets about Bernie Sanders



######################## WordCloud
### This not requires in the assignment, but still fun to do 

# based on https://youtu.be/JoArGkOpeU0

#corpus_T<-clearTweets(tweets_T, c("trump","amp","realdonaldtrump","trumptrain","donald","trumps","alwaystrump")) #remove also some campain slogans
#wordcloud(corpus_T, max.words=50)

#corpus_C<-clearTweets(tweets_C, c("hillary","amp","clinton","hillarys"))
#wordcloud(corpus_C,  max.words=50)

#corpus_B<-clearTweets(tweets_B, c("bernie", "amp", "sanders","bernies"))
#wordcloud(corpus_B,  max.words=50)
##############################

######################## Sentiment analysis

tweets_T.text <- laply(tweets_T, function(t)t$getText()) #get text out of tweets 
tweets_C.text <- laply(tweets_C, function(t)t$getText()) #get text out of tweets
tweets_B.text <- laply(tweets_B, function(t)t$getText()) #get text out of tweets



#taken from https://github.com/mjhea0/twitter-sentiment-analysis
pos <- scan('positive-words.txt', what = 'character', comment.char=';') #read the positive words
neg <- scan('negative-words.txt', what = 'character', comment.char=';') #read the negative words

source("sentiment3.R") #load algoritm
# see sentiment3.R form more information about sentiment analysis. It assigns a intereger score
# by substracitng the number of occurrence of negative words from that of positive words

analysis_T <- score.sentiment(tweets_T.text, pos, neg)
analysis_C <- score.sentiment(tweets_C.text, pos, neg)
analysis_B <- score.sentiment(tweets_B.text, pos, neg)


sem<-data.frame(analysis_T$score, analysis_C$score, analysis_B$score)


semFrame <-melt(sem, measured=c(analysis_T.score,analysis_C.score, analysis_B.score ))
names(semFrame) <- c("Candidate", "score")
semFrame$Candidate <-factor(semFrame$Candidate, labels=c("Donald Trump", "Hillary Clinton", "Bernie Sanders")) # change the labels for your celibrities

#The data you need for the analyses can be found in semFrame

```

### Homogeneity of variance analysis
Analyze the homogeneity of variance of sentiments of the tweets of the different celebrities, and provide interpretation

```{r}
#include your code and output in the document
```


### Visual inspection Mean and distribution sentiments
Graphically examine the mean and distribution sentiments of tweets for each celebrity, and provide interpretation

```{r}
#include your code and output in the document
```
### Frequentist approach

#### Linear model
Use a linear model to analyze whether the knowledge to which celebrity a tweet relates has a significant impact on explaining the sentiments of the tweets. Provide interpretation of results 

```{r}
#include your code and output in the document
```

#### Post Hoc analysis
If a model that includes the celebrity is better in explaining the sentiments of tweets than a model without such predictor, conduct a post-hoc analysis with e.g. Bonferroni correction, to examine which of celebrity tweets differ from the other celebrity tweets. Provide interpretation of the results

```{r}
#include your code and output in the document
```

#### Report section for a scientific publication
Write a small section for a scientific publication, in which you report the results of the analyses, and explain the conclusions that can be drawn.

### Bayesian Approach

#### Model description

Describe the mathematical model fitted on the most extensive model. (hint, look at the mark down file of the lectures to see example on formulate mathematical models in markdown). Justify the priors.

#### Model comparison

Conduct model analysis and provide brief interpretation of the results

```{r}
#include your code and output in the document
```

#### Comparison celebrity pair

Compare sentiments of celebrity pairs and provide a brief interpretation (e.g. CIs) 


## Question 2 - Website visits (between groups - Two factors)

### Conceptual model
Make a conceptual model underlying this research question

### Visual inspection
Graphically examine the variation in page visits for different factors levels (e.g. histogram, density plot etc.) 


```{r}
#include your code and output in the document
```


### Normality check
Visually inspect if variable page visits deviates from a Gaussian distribution, and discuss implication for general linear model analysis.


```{r}
#include your code and output in the document
```

### Frequentist Approach

#### Model analysis
Conduct a model analysis, to examine the added values of adding 2 factors and interaction between the factors in the model to predict page visits, and include brief interpretation of the results.


```{r}
#include your code and output in the document
```


#### Simple effect analysis
If the analysis shows a significant two-way interaction effect, conduct a Simple Effect analysis to explore this interaction effect in more detail.It helps first to look at the means of different conditions in a figure. Provide brief interpretation of the results.


```{r}
#include your code and output in the document
```


#### Report section for a scientific publication
Write a small section for a scientific publication, in which you report the results of the analyses, and explain the conclusions that can be drawn.

### Bayesian Approach

#### Model description

Describe the mathematical model fitted on the most extensive model. (hint, look at the mark down file of the lectures to see example on formulate mathematical models in markdown). Justify the priors.

#### Model comparison

Conduct model analysis and provide brief interpretation of the results

```{r}
#include your code and output in the document
```



# Part 3 - Multilevel model

## Visual inspection
Use graphics to inspect the distribution of the score, and relationship between session and score


```{r}
#include your code and output in the document
```

## Frequentist approach

### Multilevel analysis
Conduct multilevel analysis and calculate 95% confidence intervals, determine:

* If session has an impact on people score
* If there is significant variance between the participants in their score


```{r}
#include your code and output in the document
```

### Report section for a scientific publication
Write a small section for a scientific publication, in which you report the results of the analyses, and explain the conclusions that can be drawn.

## Bayesian approach

### Model description

Describe the mathematical model fitted on the most extensive model. (hint, look at the mark down file of the lectures to see example on formulate mathematical models in markdown). Justify the priors.

### Model comparison

Select the first 100 participants from the data set. (hint to overcome the Stan problem with a zero index, increase subject id number with 1). Compare models with with increasing complexity. 

```{r}
#include your code and output in the document
```

### Estimates examination

Examine the estimate of parameters of the model with best fitt, and provide a brief interpretation.


```{r}
#include your code and output in the document
```


